Evaluation of performances

### 2020-04-29 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

# load drake objects
loadd(
  bm_aggregated_new_buffer2
)

@@

```{r}
df <- mlr::getBMRPerformances(bm_aggregated_new_buffer2,
  "hr_buffer2", "SVM MBO No Filter",
  as.df = TRUE
)
df_tab <- df %>%
  dplyr::select(iter, rmse) %>%
  dplyr::rename(Plot = iter, RMSE = rmse) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Laukiz1 = "2", Laukiz2 = "3",
    Luiando = "1", Oiartzun = "4"
  )) %>%
  dplyr::mutate(RMSE = round(RMSE, 2))

@@

>>>>

# load drake objects
loadd(
  bm_aggregated_new_buffer2,

  # for T4
  benchmark_tune_results_hr_nri_vi
)

@@

```{r}
df <- mlr::getBMRPerformances(bm_aggregated_new_buffer2,
  "hr_buffer2", "SVM MBO No Filter",
  as.df = TRUE
)
df_tab <- df %>%
  dplyr::select(iter, rmse) %>%
  dplyr::rename(Plot = iter, RMSE = rmse) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Laukiz1 = "1", Laukiz2 = "4",
    Luiando = "3", Oiartzun = "2"
  )) %>%
  dplyr::mutate(RMSE = round(RMSE, 2))

@@

## (Table) T4 Number of features selected during tuning

The model/task combinations which were selected relate to the best performance of the respective algorithm on the HR-NRI-VI task in the overall benchmark.

```{r eval-performance-5}
bmr_inspect_tune <- mergeBenchmarkResults(benchmark_tune_results_hr_nri_vi)

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGBoost Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (%)", RMSE)

rle.lengths <- rle(df_tbl[[1]])$lengths
first <- !duplicated(df_tbl[[1]])
df_tbl[[1]][!first] <- ""

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\textbf{", df_tbl[[1]][first], "}}")
df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Percentage of selected features of each fold during optimization for selected learners",
    label = "tab:tune-perc-sel-features"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/tune-perc-sel-features.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )
```

Aggregated mean and standard deviation:

```{r}
getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF Car" = "RF MBO Car", "XGBoost Borda" = "XGBOOST MBO Borda",
    "SVM Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::group_by(Learner) %>%
  dplyr::summarise(
    "Mean (Features (%))" = mean(`Features (%)`),
    "SD (Features (%))" = sd(`Features (%)`)
  )
```
